\documentclass[12pt, a4paper]{article}
\usepackage[british]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage[en-US]{datetime2}
\pgfplotsset{/pgf/number format/use comma,compat=newest}

\title{\textbf{Discontinuous Galerkin FE approximation of elliptic problems on polyhedral grids}}
\author{Andrea Vescovini\\[1cm]{\small Supervisor: Prof. P. Antonietti}}
\DTMlangsetup{showdayofmonth=false}
\date{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\newpage
\begin{abstract}
	ciaoo
\end{abstract}
\tableofcontents
\newpage



\section*{Introduction}

\section{DG finite elments}

\section{Polyhedral grids}

\section{Implementation}
	
\section{Numerical results}

\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\begin{thebibliography}{9}
	\bibitem{review}
	Antonietti P. F., Cangiani  A., Collins J., Dong Z., Georgoulis E. H., Giani S., Houston P.: Review of discontinuous Galerkin finite element methods for partial differential equations on complicated domains. \emph{Building bridges: connections and challenges in modern approaches to numerical partial differential equations, Lecture Notes in Computational Science and Engineering}, volume 114, 279–307 (2016).
	
	\bibitem{mox}
	Antonietti, P.F., Facciola, C., Russo, A., Verani, M.: Discontinuous Galerkin approximation of flows in fractured porous media on polygonal and polyhedral meshes. \emph{MOX Report} 55/2016 (2016).
	
	\bibitem{multigrid}
	Antonietti P. F., Houston  P., Hu  X., Sarti  M., Verani M.: Multigrid algorithms for hp-version interior penalty discontinuous Galerkin methods on polygonal and	polyhedral meshes. \emph{Calcolo}, 1-30 (2017).
	
	\bibitem{hpmet}
	Cangiani A., Georgoulis E. H., Houston P.: Hp-Version discontinuous Galerkin methods on polygonal and polyhedral meshes. \emph{Mathematical Models and Methods in Applied Sciences}, 24(10), 2009-2041 (2014).
	
	\bibitem{hest}
	Hesthaven J. S., Warburton T.: \emph{Nodal Discontinuous Galerkin Methods: Algorithms, Analysis and Applications}. Springer, Berlin (2007).
	
	\bibitem{paper4}
	Giani S., Houston P.: Domain decomposition preconditioners for discontinuous Galerkin discretizations of compressible fluid flows. \emph{Numerical Mathematics: Theory, Methods and
	Applications}, 7(2), 123-128 (2014).
	
	\bibitem{Quart}
	Quarteroni A.: \emph{Numerical Models for Differetial Problems}. MS\&A, Springer-Verlag Italia, Milan (2014).
	
	\bibitem{riviere}
	Rivière B.: \emph{Discontinuous Galerkin Methods for Solving Elliptic and Parabolic Equations: Theory and Implementation}, volume 35 of \emph{Frontiers in Applied Mathematics}. Society for Industrial and Applied Mathematics (SIAM), Philadelphia, PA (2008).
\end{thebibliography}

\end{document}